---
title: "PCAdapt_teosinte.Rmd"
output: html_document
---


Load packages
```{r, setup}
library(pcadapt)
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl) # to enable 3d plots with knirt
library(ggplot2)
```

Load data. Metadata includes samples origin and PGD as extracted from raster in the script `plot_admixture_PGD_teocintles.Rmd`. 

```{r}
# genetic
parvi<- read.pcadapt(input = "../data/genetic/output/bytaxa_parviglumis.bed", type = "bed")

# meta
pgd_meta<-read.csv("../data/genetic/output/PGD_points_parvi.txt") #samples metadata are in same order than the bed file
```

Run `pcadapt` function to perform PCA and estimate K

```{r}
mypca <- pcadapt(input = parvi, K = 30)
```

Estimate the % of variation explained by the firsts components

```{r}
pc.percent<-mypca$singular.values*100
round(pc.percent, 13)
```

Perform a "scree plot’ to display in decreasing order the percentage of variance explained by each PC. The eigenvalues that correspond to random variation lie on a straight line whereas the ones that correspond to population structure lie on a steep curve. It is recommended to keep PCs that correspond to eigenvalues to the left of the straight line (Cattell’s rule). However, in a range expansion model, which seems to be the case for this taxa, there is no obvious point at which eigenvalues depart from the straight line. 

```{r}
plot(mypca, option = "screeplot")
```

Plot coloring according to sampling locations

```{r}
# Plot with sampling populations from metadata

# default
plot(mypca, option = "scores", pop= pgd_meta$POBorder)
plot(mypca, option = "scores", pop= pgd_meta$POBorder, i=9, j=13)

# custom with ggplot to explore longitude

```

Plot coloring according to PGD

```{r}
# Plot according to where samples fell in PGD 

# Get same colors than PGD map 
mycols<-data.frame(colors=c("grey70","#917031", "#4d6cd0", "#8bbb39", "#4dc0b1" , "#53d06a", "#895dc8", "#cc5658", "#d84492", "#69b974", "#d63c48", "#c556c5", "#d3542b", "#65743a", "#d2a337", "#9289cf", "#b1b23a", "#9a5398", "#498331", "#cc4668", "#37835d", "#df89be", "#dd4533", "#9b496e", "#b9b06d", "#ac575b", "#4b9cd3", "#e78b7a", "#db873d"), PGD=c(0, 5, 32, 42, 10, 86, 90, 36, 20, 48, 92, 25, 2, 11, 37, 6, 21, 43, 84, 93, 8,  38, 15, 23, 40, 58, 41, 39, 7))


# desired PGDs for scores plot (present in genetic sampling)
desired<-unique(pgd_meta$PGD_points)
mycols_desired<-mycols[mycols$PGD %in% desired, ]

mycols_desired<-mycols_desired[order(mycols_desired$PGD, na.last=TRUE), ] 
mycols_desired$colors<-as.character(mycols_desired$colors)
mycols_desired$colors


plot(mypca, option = "scores", pop= pgd_meta$PGD_points, col=mycols_desired$colors)
plot(mypca, option = "scores", pop= pgd_meta$PGD_points, i=2, j=5, col=mycols_desired$colors)
plot(mypca, option = "scores", pop= pgd_meta$PGD_points, i=1, j=3, col=mycols_desired$colors)


```


More customizable plots with ggplot

```{r}
# Get PC data is stored at mypca$scores[, i], where i is the desired PC
tab<-data.frame(PC1=mypca$scores[,1],
                PC2=mypca$scores[,2],
                PC3=mypca$scores[,3],
                pop=pgd_meta$POBorder,
                long=pgd_meta$LONGITUDE,
                PGD=as.factor(pgd_meta$PGD_points))


# plot longitude
ggplot(data = tab, aes(x=PC1, y=PC2, colour = long)) + geom_point() +
  ylab(paste0("eigenvector 1 explaining ", round(pc.percent, 2)[1], "%")) +
  xlab(paste0("eigenvector 2 explaining ", round(pc.percent, 2)[2], "%"))

```


3D plot

```{r, webgl = TRUE}

# add variable with colors
levels(tab$PGD)
tab$cols<-tab$PGD
levels(tab$cols)<-mycols_desired$colors
head(tab$cols)

plot3d(tab[, 1:3], col = tab$cols, size=3)
```

## Other plots to texplore data

```{r}
plot(mypca, option="manhattan")
plot(mypca, option="qqplot")

```

## Session details

```{bash}
sessionInfo()
```

