---
title: "plot_admixture_PGD_teocintles"
output: html_document
---

```{r}
library(raster)
library(rgdal)
library(dplyr)
library(readr)
library(ggplot2)
library(pophelper)
library(scatterpie)
library(ggnewscale)
library(gridExtra)
```

First plot CV 
```{r}
### parvi
parvi_CV<-read.delim("../data/genetic/output/admixture/parvi/Kerror_parviglumis.txt", 
                    sep=" ", header=FALSE, stringsAsFactors = FALSE) %>%
                    mutate(K = parse_number(V3)) %>% 
                    dplyr::select(K, V4) %>% rename(CV=V4)
## Plot CV
p <- ggplot(parvi_CV, aes(x=K, y=CV)) + geom_point(size=1) + geom_line()  
p + theme(axis.title.x = element_text(face="bold", size=20),
          axis.text.x  = element_text(angle=90, vjust=0.5, size=16),
          axis.title.y = element_text(face="bold", size=20),
          axis.text.y  = element_text(size=16)) +
  ggtitle(label = "Z. m. parviglumis")
```


The CV error of the Admixture analysis doesn't show a clear K value, so we chose those K values where the slope changes for each species. For ** Z. m. parviglumis** this is K=13 and K=25, and for **Z. m. mexicana** K= 5, K=10 and K=20.


## Z. m. parviglumis

Load admixture Q data and samples metadata

```{r}
# get data
parvifiles<-c("../data/genetic/output/admixture/parvi/bytaxa_parviglumis.25.Q",
              "../data/genetic/output/admixture/parvi/bytaxa_parviglumis.13.Q")
parvi_list<- readQ(parvifiles)
# Check
attributes(parvi_list)
# Get metadata
meta<-read.delim("../data/genetic/output/ADN_pasap_3604.txt")
parviPlinksamples<-read.table("../data/genetic/output/bytaxa_parviglumis.fam")
parvimeta<-meta[meta$POBL %in% parviPlinksamples$V2, ]
levels(parvimeta$ESTADO)[13]<-"EdoMex"
levels(parvimeta$ESTADO)[14]<-"Michoacan"
# add sample metadata to qlist
attributes(parvi_list[[1]])$row.names<-as.character(parvimeta$POBL)
attributes(parvi_list[[2]])$row.names<-as.character(parvimeta$POBL)
# drop unused levels
parvimeta<-droplevels(parvimeta)
```

Plot Qvals of both Ks of interest:

```{r, fig.width=30, fig.height=10}
p1 <- plotQ(alignK(parvi_list[1:2]),
            sortind = "all",
            imgoutput="join", returnplot=T, sharedindlab=FALSE,
            exportplot=F,basesize=11)
grid.arrange(p1$plot[[1]])
```

Plot only K=13 ordering by all genetic clusters

```{r, fig.width=40, fig.height=10}
p1<-plotQ(parvi_list[2],
            returnplot=T,
            exportplot=F,
            sortind = "all", basesize = 11,
           # showindlab= TRUE, useindlab=TRUE, indlabangle=90, indlabsize=0.1,
      exportpath = "../data/genetic/output/admixture/parvi")
plot(p1$plot[[1]])
```

Scatterpies of admixture groups

```{r, fig.width=15, fig.height=10}
# Read raw Qval file
Qval<-read.table(paste0("../data/genetic/output/admixture/parvi/bytaxa_parviglumis.13.Q"))
names(Qval)<-paste0("K", 1:ncol(Qval))
# add metadata
Qval<-cbind(parvimeta$POB, parvimeta$INDIV, parvimeta$LONGITUDE, parvimeta$LATITUDE, Qval)
names(Qval)[1:4]<-c("POB", "INDIV", "LONGITUDE", "LATITUDE") 
# generate same colors than the ones used for admixture plot
piecolors<-gplots::rich.colors(13)
# plot scatterpie
ppie1<- ggplot() + geom_scatterpie(data=Qval,
                           aes(x=LONGITUDE, 
                               y=LATITUDE,
                               group=POB),
                               color=NA,
                               cols=paste0("K", 1:13)) +
 scale_fill_manual(values= piecolors,
                    name="Genetic cluster") + theme_bw()
  
ppie1
```

Adding populations names:

```{r, fig.width=28, fig.height=20}
# plot scatterpie
ppie1 + geom_text(data=parvimeta,
                      aes(x=parvimeta$LONGITUDE,
                          y=parvimeta$LATITUDE,
                          label=POB),
                      color="grey40",
                     check_overlap = T,
                      hjust = 0, vjust=1, nudge_x = 0.0005,
                 size= 5.5)
```


Plot ordering populations in geographical order

```{r,fig.width=40, fig.height=12}
# Get longitudinal order
df<-data.frame(POB=parvimeta$POB, LONGITUDE=parvimeta$LONGITUDE) %>%
    unique() %>%
    arrange(LONGITUDE)
unique(df$POB)
# set levels of Pops in longitudinal order
desired_order<-unique(df$POB)
parvimeta$POBorder<-factor(parvimeta$POB, levels = desired_order)
# change levels so that they sort in that order alphabetically
levels(parvimeta$POBorder)<-paste0(1:34, levels(parvimeta$POBorder))
levels(parvimeta$POBorder)[1:9]<-paste0("0", levels(parvimeta$POBorder)[1:9])
# set labels
labset2<-data.frame(POBorder=as.character(parvimeta$POBorder), 
                    ESTADO=as.character(parvimeta$ESTADO), stringsAsFactors = FALSE)
#plot
p<-plotQ(parvi_list[2],
            returnplot=T,
            exportplot=F,
            sortind = "all",
      grplab=labset2, 
      ordergrp=TRUE, 
      grplabangle= 45, grplabsize=10, linesize=2, divsize = 2, grplabheight= 2, grplabpos=0.5,
      exportpath = "../data/genetic/output/admixture/parvi")
plot(p$plot[[1]])
```


Extract in which PGD do the sampled individuals fall. This would be used to then add this information to the plot and see how well PGD correspond to genetic clusters.

First load raster data of Zea mays spp parviglumis SDM and the PGD that fell within it:

```{r}
# path to rasters
my_rasters<-c("../data/spatial/modelosDarwinZea/Zea_mays_parviglumis.tif", # SDM 
              "../data/spatial/areasProxyDivGen/crop_to_sp_final/PDG_Zea_mays_parviglumis.tif") #SDM subdivied by Proxies of gen div
# stack rasters and add nicer name
parvi_rasters<-stack(my_rasters)
# check
names(parvi_rasters)
# Check projection
proj4string(parvi_rasters$PDG_Zea_mays_parviglumis)
# change projection to longlat for nicer visualization
newcrs <- CRS("+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")
parvi_rasters<-projectRaster(parvi_rasters, crs=newcrs, method="ngb")
parvi_rasters<-stack(parvi_rasters)
```

Z. m. parviglumis has `r length(unique(getValues(parvi_rasters$PDG_Zea_mays_parviglumis)))-1` PGD distributed like this:

```{r}
# Get number of cells of each PDG
table(getValues(parvi_rasters$PDG_Zea_mays_parviglumis))
```


Plot PGD and sampling points of genetic data.

```{r, fig.width=15, fig.height=10}
# crop raster to make it more managable
parvi_small<- raster::crop(parvi_rasters$PDG_Zea_mays_parviglumis,
                           y=extent(c(-107, -96 , 15.5, 22)))
# convert to df to plot with ggplot
raster_df<-as.data.frame(rasterToPoints(parvi_small, spatial = TRUE))
raster_df$PDG_Zea_mays_parviglumis<-as.character(raster_df$PDG_Zea_mays_parviglumis)
# get nice colors
mycols<-c("grey40","#917031", "#4d6cd0", "#8bbb39", "#c556c5", "#53d06a", "#895dc8", "#42a331", "#d84492", "#69b974", "#d63c48", "#4dc0b1", "#d3542b", "#4b9cd3", "#d2a337", "#9289cf", "#b1b23a", "#9a5398", "#498331", "#cc4668", "#37835d", "#df89be", "#6e7721", "#9b496e", "#b9b06d", "#ac575b", "#65743a", "#e78b7a", "#db873d", "#a2552d")
# get labels with 0 as "NA" (it is not really NA, just the part of Mx out of the species range). True NA is outside of Mx.
mylabs<-unique(getValues(parvi_rasters$PDG_Zea_mays_parviglumis))[2:length(unique(getValues(parvi_rasters$PDG_Zea_mays_parviglumis)))] # ommit the first (true NA)
mylabs[1]<-"NA" # change 0 to "NA"
mylabs
# plot PGD raster
p<- ggplot() +
    geom_raster(data = raster_df , aes(x = x, y = y, fill = PDG_Zea_mays_parviglumis)) +
    scale_fill_manual(values= alpha(mycols, 0.5) , name="PGD",
                      labels=mylabs) + # no prevent the area outside the SDM to appear as a PDG 0
    theme_bw() + 
    labs(x="", y= "") + theme(text = element_text(size = 25))
# add sampling points
p + geom_point(data=parvimeta, aes(x=LONGITUDE, 
                                   y=LATITUDE))
```

Plot scatterpies with genetic groups

```{r, fig.width=15, fig.height=10}
p_piemap<-p + new_scale("fill") + # this is needed because raster and pie have diff fills
          geom_scatterpie(data=Qval,
                                   aes(x=LONGITUDE, 
                                       y=LATITUDE,
                                       group=POB),
                                       color="NA",
                                       cols=paste0("K", 1:13)) +
         scale_fill_manual(values= piecolors,
                            name="Genetic cluster") +
          labs(x="", y= "") + theme(text = element_text(size = 25))
p_piemap
```


Extract in which PGD each genetic sample falls:

```{r}
# Create function to estimate the mode, omitting na values
Mode <- function(x) {
  ux <- unique(na.omit(x))
  ux[which.max(tabulate(match(x, ux)))]
}
# transform 0 value (out of sp SDM range) to NA so that only PGD are considered
parvi_rasters$PDG_Zea_mays_parviglumis<-reclassify(parvi_rasters$PDG_Zea_mays_parviglumis, 
                                                   rcl=c(0, .1, NA), include.lowest=TRUE)
# extract the PDG most frequent in a given buffer radio of the sampling point
# ignoring NA values (see Mode fun)
PGD_points<-raster::extract(parvi_rasters$PDG_Zea_mays_parviglumis,
                            buffer=2500, fun=Mode, # so that no points fell in only NAs
                    y=data.frame(long=parvimeta$LONGITUDE,
                                 lat=parvimeta$LATITUDE)) %>%
            as.character()
PGD_points<-parvimeta %>% dplyr::select(LONGITUDE, LATITUDE, DNASample, POB, POBorder, POBL) %>%
                  mutate(PGD_points=PGD_points) 
table(PGD_points$PGD_points)
# check if there are samples that did not fell in any PGD
sum(is.na(PGD_points$PGD_points)) 
PGD_points[is.na(PGD_points$PGD_points), ]
```

Remove genetic samples that did not fell in any PGD

```{r}
# check original n
nrow(PGD_points)
# get samples names that FELL in PGD
PGD_points<-PGD_points[!is.na(PGD_points$PGD_points), ]
fell_in_PGD<-as.character(PGD_points$POBL)
# check how many samples we have now
length(fell_in_PGD)
# keep only samples that fell in PGD in the admixture data
# get rows matching fell in PGD
x<-attributes(parvi_list[[2]])$row.names %in% fell_in_PGD
# subset list
subset_admix_list<-list(parvi_list[[2]][x,])
names(subset_admix_list)<-names(parvi_list[2])
```

Use this information to see in which genetic group our PGD fall:

```{r, fig.width=40, fig.height=10}
## order PGD
# set levels of PGD more or less in lontigitudinal order
desired_order<-c("48", "36", "10", "5", "15", "11" , "37", "6", "84", "43", "8", "40", "41")
PGD_points$PGD_order<-factor(PGD_points$PGD_points, levels = desired_order)
# change levels so that they sort in that order alphabetically
levels(PGD_points$PGD_order)<-paste0(1:13, "_",levels(PGD_points$PGD_order))
levels(PGD_points$PGD_order)[1:9]<-paste0("0", levels(PGD_points$PGD_order)[1:9])
# set labels
labsetPGD<-data.frame(PGD_points=as.character(PGD_points$PGD_order),
                      POBorder=as.character(PGD_points$POBorder),
                      stringsAsFactors = FALSE)
p3<-plotQ(subset_admix_list[1],
            returnplot=T,
            exportplot=F,
            sortind = "all",
      grplab=labsetPGD, selgrp = "PGD_points",
      ordergrp=T, 
      grplabangle= 90, grplabsize=8, linesize=3, divsize = 3.5,
      exportpath = getwd(), height = 20, width = 80)
plot(p3$plot[[1]])
```

Omit labels for plot for the paper and save as png:

```{r, fig.width=30, fig.height=5}
p3<-plotQ(subset_admix_list[1], 
            returnplot=T,
            exportplot=T,
            sortind = "all",
      grplab=labsetPGD, selgrp = "PGD_points",
      ordergrp=T, 
      grplabangle= 90, grplabsize=8, divsize = 1,
      showgrplab= FALSE, splab="",
      exportpath = getwd(), height = 2.5, width = 15,
      outputfilename="../figures/parviglumis13Q_subsetPGD")
```

Save map for paper plot:

```{r, fig.height = 10, fig.width = 15}
p_piemap<-p + theme(legend.position = "none") +
          new_scale("fill") + # this is needed because raster and pie have diff fills
          geom_scatterpie(data=Qval,
                                   aes(x=LONGITUDE, 
                                       y=LATITUDE,
                                       group=POB),
                                       color="NA",
                                       cols=paste0("K", 1:13)) +
         scale_fill_manual(values= piecolors)+
         labs(x="", y= "") + theme(text = element_text(size = 15))
# save to file
ggsave("../figures/piemap_parviglumis_pgd.png",
       plot=p_piemap, dpi=72,
       width=15, height = 10, units="cm")
```

Get session info:

```{r}
sessionInfo()
```